GravExplain: Continuous gravitational wave searches in a table-top experiment

### 2020-02-07 paper/paper_main.tex
69th day of Summer

\begin{figure}
	\includegraphics[width=0.8\textwidth]{ifo_schematic_webcam.pdf}
	\caption{Michelson interferometer schematic, interference pattern is recorded by a webcam}
	\label{fig:ifo_schematic_webcam}
\end{figure}
% Note that we do not include the common compensating plate that equalises the amount of time spent in glass for each beam. We did not find it necessary to include it to be able to demonstrate the results desired.

@@

\begin{figure}
	\includegraphics[width=\textwidth]{webcam_still0.pdf}
	\caption{Interference pattern from Michelson interferometer as viewed by webcam from below (hence why the pattern appears non-circular), red dot indicates point where intensity time series was measured, the central fringe is approximately 5mm across}
	\label{fig:interference_pattern}
\end{figure}

@@

\begin{figure}
	\includegraphics[width=\textwidth]{webcam_expt_4_0209-cropped.pdf}
	\caption{Spectrum of intensity time series of interference pattern as captured by a webcam for an injected tone of 2.09Hz hitting the interferometer, injected fundamental frequency and harmonics thereof clearly present in spectrum}
	\label{fig:webcam_spectrum}
\end{figure}

@@

\begin{figure}
	\includegraphics[width=\textwidth]{expt_overlay_2_viterbi_test_webcam.pdf}
	\caption{Spectrogram of observed signal overlaid with white crosses for the Viterbi path and pink dots for the injected signal, notice the high correlation between them indicating that the signal is able to be recovered; also note the deviation at the start when the signal moves too quickly and just before the background anomaly at 150s}
	\label{fig:viterbi_overlay}
\end{figure}

@@

\begin{figure}
	\includegraphics[width=0.8\textwidth]{ifo_schematic_photodiode.pdf}
	\caption{Michelson interferometer schematic, a part of the interference pattern is recorded by a photodiode}
	\label{fig:ifo_schematic_podo}
\end{figure}

@@

\begin{figure}%[H]
	\includegraphics[width=\textwidth]{podo_noise_psd_zoom-cropped.pdf}
	\caption{Power spectral density (PSD) of the optical microphone system with no injected audio (i.e.\ with the speaker off), show high power in the 50Hz mains hum and its harmonics (most likely from the photodiode circuit and the ambient lighting), otherwise is a fairly white spectrum except for the broad, shallow maximum at 750Hz}
	\label{fig:psd_noise}
\end{figure}

@@

\begin{figure}%[H]
	\includegraphics[width=0.8\textwidth]{butterworth_150_3000-cropped.pdf}
	\caption{Butterworth bandpass filter frequency response, green vertical lines show the band limits of 150Hz and 3kHz. Note the very flat response within the band, any amplitude beyond -3dB is significant attenuation.}
	\label{fig:butterworth}
\end{figure}

@@

\begin{figure}%[H]
	\includegraphics[width=\textwidth]{filter_timeseries_aa_melatos-cropped.pdf}
	\caption{Optical microphone recording of adult male voice (saying ``A cathode ...'') shown before (top) and after (bottom) logMMSE filter is applied, only one second of the one minute recording is shown. The bump at the start of the time series is the result of filtering a finite signal, and is expected.}
	\label{fig:logMMSE_timeseries}
\end{figure}

\begin{figure}%[H]
	\includegraphics[width=\textwidth]{filter_spectrum_aa_melatos-cropped.pdf}
	\caption{Spectrum of optical microphone recording of adult male voice shown before (top) and after (bottom) logMMSE filter is applied, showing only up to 2kHz and a detail of the spectrum (limited to show only up to amplitude 2, while before filtering the 50Hz line has an amplitude of 40)}
	\label{fig:logMMSE_spectrum}
\end{figure}

@@

\begin{figure}%[H]
	\includegraphics[width=\textwidth]{circuit_diagram_2.pdf}
	\caption{Circuit diagram for photodiode reading. Photodiode in reverse-bias over an op-amp, analog signal then passed through Sallen-Key anti-aliasing filter tuned to 16kHz, then into an analog-to-digital converter (ADC), that’s finally read by the special purpose input (SPI) pins of a Raspberry Pi}
	\label{fig:circuit_diagram}
\end{figure}

>>>>

\begin{figure}
	\includegraphics[width=0.8\textwidth]{figures/ifo_schematic_webcam.pdf}
	\caption{Michelson interferometer schematic, interference pattern is recorded by a webcam}
	\label{fig:ifo_schematic_webcam}
\end{figure}
% Note that we do not include the common compensating plate that equalises the amount of time spent in glass for each beam. We did not find it necessary to include it to be able to demonstrate the results desired.

@@

\begin{figure}
	\includegraphics[width=\textwidth]{figures/webcam_still0.pdf}
	\caption{Interference pattern from Michelson interferometer as viewed by webcam from below (hence why the pattern appears non-circular), red dot indicates point where intensity time series was measured, the central fringe is approximately 5mm across}
	\label{fig:interference_pattern}
\end{figure}

@@

\begin{figure}
	\includegraphics[width=\textwidth]{figures/webcam_expt_4_0209-cropped.pdf}
	\caption{Spectrum of intensity time series of interference pattern as captured by a webcam for an injected tone of 2.09Hz hitting the interferometer, injected fundamental frequency and harmonics thereof clearly present in spectrum}
	\label{fig:webcam_spectrum}
\end{figure}

@@

\begin{figure}
	\includegraphics[width=\textwidth]{figures/expt_overlay_2_viterbi_test_webcam.pdf}
	\caption{Spectrogram of observed signal overlaid with white crosses for the Viterbi path and pink dots for the injected signal, notice the high correlation between them indicating that the signal is able to be recovered; also note the deviation at the start when the signal moves too quickly and just before the background anomaly at 150s}
	\label{fig:viterbi_overlay}
\end{figure}

@@

\begin{figure}
	\includegraphics[width=0.8\textwidth]{figures/ifo_schematic_photodiode.pdf}
	\caption{Michelson interferometer schematic, a part of the interference pattern is recorded by a photodiode}
	\label{fig:ifo_schematic_podo}
\end{figure}

@@

\begin{figure}%[H]
	\includegraphics[width=\textwidth]{figures/podo_noise_psd_zoom-cropped.pdf}
	\caption{Power spectral density (PSD) of the optical microphone system with no injected audio (i.e.\ with the speaker off), show high power in the 50Hz mains hum and its harmonics (most likely from the photodiode circuit and the ambient lighting), otherwise is a fairly white spectrum except for the broad, shallow maximum at 750Hz}
	\label{fig:psd_noise}
\end{figure}

@@

\begin{figure}%[H]
	\includegraphics[width=0.8\textwidth]{figures/butterworth_150_3000-cropped.pdf}
	\caption{Butterworth bandpass filter frequency response, green vertical lines show the band limits of 150Hz and 3kHz. Note the very flat response within the band, any amplitude beyond -3dB is significant attenuation.}
	\label{fig:butterworth}
\end{figure}

@@

\begin{figure}%[H]
	\includegraphics[width=\textwidth]{figures/filter_timeseries_aa_melatos-cropped.pdf}
	\caption{Optical microphone recording of adult male voice (saying ``A cathode ...'') shown before (top) and after (bottom) logMMSE filter is applied, only one second of the one minute recording is shown. The bump at the start of the time series is the result of filtering a finite signal, and is expected.}
	\label{fig:logMMSE_timeseries}
\end{figure}

\begin{figure}%[H]
	\includegraphics[width=\textwidth]{figures/filter_spectrum_aa_melatos-cropped.pdf}
	\caption{Spectrum of optical microphone recording of adult male voice shown before (top) and after (bottom) logMMSE filter is applied, showing only up to 2kHz and a detail of the spectrum (limited to show only up to amplitude 2, while before filtering the 50Hz line has an amplitude of 40)}
	\label{fig:logMMSE_spectrum}
\end{figure}

@@

\begin{figure}%[H]
	\includegraphics[width=\textwidth]{figures/circuit_diagram_2.pdf}
	\caption{Circuit diagram for photodiode reading. Photodiode in reverse-bias over an op-amp, analog signal then passed through Sallen-Key anti-aliasing filter tuned to 16kHz, then into an analog-to-digital converter (ADC), that’s finally read by the special purpose input (SPI) pins of a Raspberry Pi}
	\label{fig:circuit_diagram}
\end{figure}
